---
title: "03_DataWranglingIII"
author: "Mariana Higashi Sakamoto"
date: "27/11/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---


## Including Plots

You can also embed plots, for example:

```{r pressure, warnings=False}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


You can format texts:

- *italic*: * at the beginning and end of sentence

- **bold**: addind ** at the beginning and end of sentence

- To create bullet points just do: * at the beginning of the sentence

* Title 1

* Title 2

  * Subtitle 2
  
  To do that give a tab
  
To write something at the bottom use ~ at the beginnig and end of element
H~2~O

To write something at the top use ^ at the beginnig and end of element
a^2^+b^2^ = c^2^

You can use LaTex format to write equations
For example:
$a=b^2$
to write in the same line
$$ a = \sqrt{b}+c^2$$
$$ a = ({b} \times {c})+ (\dfrac {d}{e})$$
$$ \alpha_1 = \beta_1 + \beta_2^3 $$

Introducing chunks: thats where we are going to code
```{r}
array <- c(1:5)
array
```

Now lets import packages and a dataset
```{r open Dataset, echo=TRUE, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(knitr)
dados <- read_excel("./02_DataWrangling/(1.2) Dataset Aula Data Wrangling.xls")
head(dados)
```
Create a table
```{r create a table}
dados_1 <- dados %>%rename(time = `Tempo para chegar à escola (minutos)` , 
                 distance = `Distância percorrida até a escola (quilômetros)`) 

dados_1  %>% 
  summarise(ave_time = mean(time),
            ave_dist = mean(distance)) %>% kable()
```

Create a graph
```{r Create a plot}
dados_1 %>% ggplot() + geom_point(aes(x=distance, y= time))
```

To be able to export as a pdf install:
if tinytex:::is_tinytex()
# tinytex::install_tinytex()




