---
title: "Spatial Analysis III"
output: html_notebook
---
### Setting up the libraries
```{r warning=FALSE}
pacotes <- c("rgdal","plotly","tidyverse","knitr","kableExtra","gridExtra",
             "png","grid","magick","rgl","devtools","GISTools","rayshader",
             "tmap","broom")

if(sum(as.numeric(!pacotes %in% installed.packages())) != 0){
  instalador <- pacotes[!pacotes %in% installed.packages()]
  for(i in 1:length(instalador)) {
    install.packages(instalador, dependencies = T)
    break()}
  sapply(pacotes, require, character = T) 
} else {
  sapply(pacotes, require, character = T) 
}
```

### 1. Loading the shapefile from Santa Catarina State, Brazil and the poverty data

```{r }
shp_sc <- readOGR(dsn = "E:/DataScienceMBA/RStudio/03_SpatialAnalysis/shapefile_sc",
                  layer = "sc_state")

load("E:/DataScienceMBA/RStudio/03_SpatialAnalysis/dados_sc.RData")

dados_sc %>% 
  kable() %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = TRUE, 
                font_size = 12) # Contain city name and poverty index

summary(dados_sc)
```
### 2. Creating a dataframe from the shapefile and merging 
```{r}

shp_sc_df <- tidy(shp_sc, region = "CD_GEOCMU") %>% 
  rename(CD_GEOCMU = id)

shp_sc_df <- shp_sc_df %>% 
  left_join(dados_sc, by = "CD_GEOCMU")

```
### 3. Plotting the poverty map in Santa Catarina

```{r }
mapa_sc <- shp_sc_df %>%
  ggplot(aes(x = long,
           y = lat, 
           group = group, 
           fill = poverty)) +
  geom_polygon() +
  scale_fill_gradient(limits = range(shp_sc_df$poverty),
                      low = "#FFF3B0", 
                      high="#E09F3E") +
  layer(geom = "path", 
        stat = "identity", 
        position = "identity",
        mapping = aes(x = long, 
                      y = lat, 
                      group = group, 
                      color = I('#FFFFFF'))) +
  theme(legend.position = "none", 
        axis.line = element_blank(), 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(), 
        axis.title.y = element_blank(),
        axis.ticks = element_blank(), 
        panel.background = element_blank())

mapa_sc %>% plot()
```
### 4. Saving map as png

```{r}
# Minimun and maximun of lattitude and longitude
xlim <- ggplot_build(mapa_sc)$layout$panel_scales_x[[1]]$range$range
ylim <- ggplot_build(mapa_sc)$layout$panel_scales_y[[1]]$range$range

ggsave(filename = "mapa_co_dsa.png",
       width = diff(xlim) * 4, 
       height = diff(ylim) * 4, 
       units = "cm")
```


### 5. Reading the image again. 
Note that our intention is to plot the same map with the poverty rate as the z-index 
```{r}
#readig the png
background_mapa <- readPNG("mapa_co_dsa.png")

# Capturing the coorditates and centroid (variable CD_GEOCMU) into a dataframe
coordinates(shp_sc) %>% 
  data.frame() %>% 
  rename(longitude = 1,
         latitude = 2) %>% 
  mutate(CD_GEOCMU = shp_sc@data$CD_GEOCMU) %>% 
  dplyr::select(latitude, everything()) -> coords_sc
```

### 6. Merging the dataframe containing the centroids to the dataframe containg the gemetry of city limits in Santa Catarina
```{r}

shp_sc_df <- shp_sc_df %>% 
  left_join(coords_sc, by = "CD_GEOCMU")

head(shp_sc_df)
```
### 7. Georeferring the PNG image and plotting the poverty index in each city centroid. 
Note we are plotting the dataframe and the image together by 
```{r warning=FALSE}
mapa_pobreza <- shp_sc_df %>%
  ggplot() + 
  annotation_custom(
    rasterGrob(background_mapa, 
               width=unit(1,"npc"),
               height=unit(1,"npc")),-Inf, Inf, -Inf, Inf) + 
  xlim(xlim[1],xlim[2]) + # x-axis Mapping
  ylim(ylim[1],ylim[2]) + # y-axis Mapping
  geom_point(aes(x = longitude, y = latitude, color = poverty), size = 1.5) + 
  scale_colour_gradient(name = "Poverty", 
                        limits = range(shp_sc_df$poverty), 
                        low = "#FCB9B2", 
                        high = "#B23A48") + 
  theme(axis.line = element_blank(), 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(), 
        axis.title.y = element_blank(),
        axis.ticks = element_blank(), 
        panel.background = element_blank())

mapa_pobreza %>% plot()
```
### 8. Generating a 3D map
```{r }
options(rgl.useNULL = TRUE) # Suppress the separate window.
library(rgl)

plot_gg(ggobj = mapa_pobreza, 
        width = 11, 
        height = 6, 
        scale = 300, 
        multicore = TRUE
        )

rglwidget()

```



