---
title: "World Data Index"
author: "Mariana Higashi Sakamoto"
date: "27/11/2021"
output: html_document
---

#1. Importing the data

```{r ImportingData}
library(tidyverse) #to use pipe
library(readxl)
wdiDataset <- read_excel("(3.2) WDI World Bank Wrangling.xlsx")
glimpse(wdiDataset)
head(wdiDataset)

```

#2. Changing the structure of the dataset
Here we only have 6 columns, and some variable names are on the rows (Series Name). We will try to verticalize the table so it is easier to make analisys with it.
```{r OrganizingData}
length(unique(wdiDataset$`Country Name`))
length(unique(wdiDataset$`Series Name`))
length(unique(wdiDataset$`Series Code`))
length(unique(wdiDataset$Topic))

wdiDataset <- wdiDataset %>% rename(country = 1, 
                                    country_cod = 2, 
                                    series = 3,
                                    series_cod = 4, 
                                    YR2019 = 5,
                                    topic = 6)
glimpse(wdiDataset)

```
2.1 Converting char to numeric

```{r}
wdiDataset <- wdiDataset %>% mutate(YR2019 = na_if(YR2019, ".."))
YR2019_num <- as.numeric(wdiDataset$YR2019)
wdiDataset <- wdiDataset %>% mutate(YR2019_num) %>% 
  select(everything(), -YR2019, YR2019_num)
glimpse(wdiDataset)
```
#3. Filtering only Health topics

```{r}
wdiHealth <- wdiDataset %>% filter(str_detect(topic, '^Health')) # ^filter all observations that begin with Health
unique(wdiHealth$topic)
glimpse(wdiHealth)
```
#4. Make dataset wider (rows into variables) 
```{r}
wdiHealth_wide <- pivot_wider(wdiHealth, id_cols = c("country","country_cod", "topic"),
                                       names_from = "series", 
                                       values_from = "YR2019_num")
head(wdiHealth_wide)

```
# 5. Adding information about PIB income group into the dataset
```{r}
income <- read_excel("(2.3) WBD PIB per CApita.xls")
glimpse(income)
healthIncome <- wdiHealth_wide %>% rename("Country Code" = country_cod) %>% 
  left_join(income, by = "Country Code") %>% 
  select(everything(), -c("Country Name", "2019"))

#Counting the NA values in each row
NA_count <- healthIncome %>% summarise_all(~ sum(is.na(.)))

filter_relevant <- colnames(NA_count[1,])[(NA_count[1,] < 2600)]
filter_relevant

healthIncome %>%  select(everything(), -c(filter_relevant))


```


