---
title: "Statistics Fundamentals"
author: "Mariana Higashi Sakamoto"
date: "04/12/2021"
output: html_document
---

#1. Question
In the analysis of the granting of loans, a potentially important variable is the person's
income. The manager of a bank collects a database from their account holders and
extracts the variable “monthly income (R$)” for 50 people. Although it is a quantitative
variable, they want to perform an analysis through a frequency table. Therefore, it is
asked:
  a) Classify the account holders in the income ranges, being: 0-2,000; 2,001-4.000;
4.001- 6.001-8.000; 8.001-10.000 and 10.001-12.000.
  b) Next, elaborate the frequency table for the income ranges above.
  
##Solution
First, lets read the data and order them
```{r}
library(tidyverse)
library(dplyr)
library(readr)
STATQ1_Income <- read_delim("E:/DataScienceMBA/RStudio/DataScienceMBA/DataSource/STATQ1_Income.csv", 
+     ";", escape_double = FALSE, col_types = cols(Observacao = col_integer()), 
+     locale = locale(decimal_mark = ","), 
+     trim_ws = TRUE)
STATQ1_Income$Renda

names(STATQ1_Income) <- c('id', 'income')


income <- STATQ1_Income[order(STATQ1_Income$income, decreasing = T),]
head(income)

```
Now, lets group them in factors

```{r}
income_ds <- income %>% mutate(income_rate = case_when(c(income) <= 2000 ~'0-2.000',
                                          c(income) <= 4000 ~'2.001-4.000',
                                          c(income) <= 6000 ~'4.001-6.000',
                                          c(income) <= 8000 ~'6.001-8.000',
                                          c(income) <= 10000 ~'8.001-10.000',
                                        c(income) > 10000 ~'10.001-12.000'
                                          ))
income_ds$income_rate <- factor(income_ds$income_rate ,levels =  c('0-2.000',
                                  '2.001-4.000',
                                  '4.001-6.000',
                                  '6.001-8.000',
                                  '8.001-10.000',
                                  '10.001-12.000')
  )
sample_total <- nrow(income_ds)
sample_total


income_summary <- income_ds %>% group_by(income_rate) %>% 
  summarise(freq = n(), relative_freq = n()/sample_total*100) %>%
  ungroup() %>% 
  droplevels(.)
income_summary
```


```{r}

income_summary %>% 
  ggplot(aes(income_rate,freq))+
  geom_col() +
  labs(title="Customers Income", x= "Income Rate", y = "Frequency")+
  geom_text(aes(label = signif(freq, digits = 3)), nudge_y = 1)

```

