---
title: "Question 11"
author: "Mariana Higashi Sakamoto"
date: "16/01/2022"
output: html_document
---

## Question 11
In the food industry, for the preparation of a certain product, the standard amount of  salt is 8g with a standard deviation equal to 1g. In the analysis of a sample of 85 products, an average amount of salt was observed of 8.25g. 

Evaluate if the amount observed in the sample can be considered statistically major, at the level of significance of 5%.

## Answer

Z-test is used for it when sample size is large, generally n >30. Whereas t-test is used for hypothesis testing when sample size is small, usually n < 30 where n is used to quantify the sample size.

```{r}
salt_exp <- 8
n <- 85
salt_obs <- 8.25
sd_obs <- 1

Zscore <- (salt_obs - salt_exp) / sqrt(sd_obs/n)
Zscore

pval <-  1 - dnorm(Zscore, mean = 0, sd = sd_obs)
pval

crit_val <- qnorm(0.05,  lower.tail = F)
crit_val
```

As the p-value is less than 5% or also the t-value is in the Critical Area [-2.3,+2,3], the mean is not statistically equal and the Yogurt has more calories than it says on average.

```{r}
library(ggplot2)

z <- seq (-4,4, by=0.01) 
fz <- dnorm(z, mean = 0, sd = 1)

x <- seq(crit_val, 4, 0.1)
y <- c(dnorm( x, mean = 0, sd = 1), 0,0)
x <- c(x, 4, crit_val)

ggplot() + geom_line(aes(z, fz)) +
           geom_polygon(data = data.frame(x=x, y=y), aes(x, y), fill='blue')

```
```

