---
title: "question 6 - Normal Distribution"
author: "Mariana Higashi Sakamoto"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question 6. 
In the last months, the time was measured between the beginning and end of one of 
the stages of the production process of a certain product. The average time was 
calculated in 26.5 minutes and the standard deviation was 4.0 minutes. Knowing that 
this variable follows a normal distribution, identify the following information:

  a) P(X>37)
  b) P(X<20)
  c) P(22<X<28)
  
## Answer

** a) **
We look at the steps necessary to calculate the p value for a particular test. In question a, we want to calculate the probability of an observation is higher than 37 min.
```{r}
# Sample information:
aveTime <- 26.5
sdTime <- 4

# We want to calulate the Z-score associated to 37 min. The Z-score is found by assuming that the null hypothesis is true, subtracting the assumed mean, and dividing by the theoretical standard deviation.
N <- 37
Z <- (N - aveTime)/sdTime
print(Z)

#  If the Z-score that is found is positive then we need to take one minus the associated probability. Also, for a two sided test we need to multiply the result by two. Not the case here. 
pValue <- (1 - pnorm(Z))
pValue


# The probability of the time average being more than 37 minutes is 0,43%
```

```{r}
library(ggplot2)

z <- seq(0,50,0.01)
fz <- dnorm(z, mean = aveTime, sd = sdTime)
q <- N
x <- seq( q, 50, 0.01)
y <- c(dnorm(x, mean = aveTime, sd = sdTime), 0, 0)
x <- c(x, q ,q)
ggplot() + geom_line(aes(z, fz)) +
           geom_polygon(data = data.frame(x=x, y=y), aes(x, y), fill='blue')
```


** b) **
```{r}
# Now we want to calulate the Z-score associated to 20 min. The Z-score is found by assuming that the null hypothesis is true, subtracting the assumed mean, and dividing by the theoretical standard deviation.
N <- 20
Z <- (N - aveTime)/sdTime
print(Z)
#  As the Z-score that is found negative then we need to take one minus the associated probability.

pValue <- (pnorm(Z))
pValue

# The probability of the time average being less than 20 minutes is 5.21%
```

```{r}
library(ggplot2)

z <- seq(0,50,0.01)
fz <- dnorm(z, mean = aveTime, sd = sdTime)
q <- N
x <- seq(0, q, 0.01)
y <- c(dnorm(x, mean = aveTime, sd = sdTime), 0, 0)
x <- c(x, q,0)
ggplot() + geom_line(aes(z, fz)) +
           geom_polygon(data = data.frame(x=x, y=y), aes(x, y), fill='blue')
```

** c) **
```{r}
# Now we want to calulate the Z-score associated to 22 and 28 min. The Z-score is found by assuming that the null hypothesis is true, subtracting the assumed mean, and dividing by the theoretical standard deviation.
N1 <- 22
N2 <-28

Z1 <- (N1 - aveTime)/sdTime
Z2 <- (N2 - aveTime)/sdTime

print(Z1)
print(Z2)
#  As the Z-score that is found negative then we need to take one minus the associated probability.

pValue1 <- (pnorm(Z1))

pValue2 <- pnorm(Z2)
pValue2

pValue <-  pValue2 - pValue1
pValue

```

```{r}
library(ggplot2)

z <- seq(0,50,0.01)
fz <- dnorm(z, mean = aveTime, sd = sdTime)
x <- seq(N1, N2, 0.01)
y <- c(dnorm(x, mean = aveTime, sd = sdTime), 0, 0)
x <- c(x, N2,N1)

ggplot() + geom_line(aes(z, fz)) +
           geom_polygon(data = data.frame(x=x, y=y), aes(x, y), fill='blue')
```