---
title: "Question 9"
author: "Mariana Higashi Sakamoto"
date: "16/01/2022"
output: html_document
---

## Question 9
Source: Fávero and Belfiore, 2017, Cap. 7) 
It is desired to compare the average time for service (min) in 2 hospitals.
To do this, a sample was collected with 20 patients in each hospital.

Check if there are differences between the average times of waiting in two hospitals. 

Consider α = 1%.

Additionally, calculate the confidence intervals for the average time for waiting in the two hospitals


```{r}
hosp1 <- c(72,	58,	91,	88,	70,	76,	98,	101,	65,	73,	79,	82,	80,	91,	93,	88,	97,	83,	71,	74)
hosp2 <- c(66,	40,	55,	70,	76,	61,	53,	50,	47,	61,	52,	48,	60,	72,	57,	70,	66,	55,	46,	51)

# mean time from hospital 1
mean(hosp1)
# mean time from hospital 2
mean(hosp2)
# var time from hospital 1
var(hosp1)
# var time from hospital 2
var(hosp2)
```

Test the normality of the samples:
```{r}

qqnorm(hosp1, pch = 1, frame = FALSE)
qqline(hosp1, col = "steelblue", lwd = 2)

shapiro.test(hosp1) #since p-value is bigger than 5% it can be considered normal

qqnorm(hosp2, pch = 1, frame = FALSE)
qqline(hosp2, col = "steelblue", lwd = 2)

shapiro.test(hosp2)#since p-value is bigger than 5% it can be considered normal


```

1. Test of the Variances
Variance test to check if they are statistically equal or hosp 1 is greater then hosp 2
```{r}
var.test(hosp1, hosp2, alternative = "greater")
```
Because the p-values is greater than 5%, the null hipothesis is not rejected

2. Test of Averages

**The unpaired two-samples t-test is used to compare the mean of two independent groups.**

Note that, unpaired two-samples t-test can be used only under certain conditions:

when the two groups of samples (A and B), being compared, are normally distributed. This can be checked using Shapiro-Wilk test.
and when the variances of the two groups are equal. This can be checked using F-test.

```{r}
t.test(hosp1,hosp2, conf.level = 0.99)
```
As the p-values is less than 1%, we reject the null hypothesis and we can say that their average are statistically different.


To get the interval of confidence of 1%

```{r}
ttest1 <- t.test(hosp1, conf.level = 0.99)
ttest2 <- t.test(hosp2, conf.level = 0.99)

ttest1$conf.int
ttest2$conf.int
```
Source: 
http://www.sthda.com/english/wiki/unpaired-two-samples-t-test-in-r

