---
title: "Question 4 - Statistics"
author: "Mariana Higashi Sakamoto"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Question 4
(Source: Fávero and Belfiore, 2017, Cap. 5) Suppose a student answer right three questions for each five tests. Being X the number of attempts up to the 12th right one.
Determine the probability of the student needing to do 20 questions to get 12 right.
### Review

Negative Binomial Distribution
This time, we want to analyze how many independent Bernoulli experiments (x) is needed to obtain k successes.

This distribution differs from the Binomial Distribution:
  **Binomial**: distribution of the number of successes in a fixed number of independent Bernoulli trials
  **Negative Binomial**: distribution of the number of trials (or failures) needed to get a fixed number of successes

$$ P(X=x)=\left( ^{x-1}_{k-1}\right).p^k.(1-p)^{x-k}  $$
Where $(^{x-1}_{k-1}) = \dfrac{(x-1)!}{(k-1)![(x-1)-(k-1)]!}$

### Answer
```{r}
r <- 12
p <- 3/5
n <- 20 - r

# exact
P1<- dnbinom(x = n, size = r, prob = p)
P1*100

P2 <- factorial(x-1)/( (factorial(k-1)*factorial((x-1)-(k-1))))*p^k*(1-p)^(x-k)
P2*100

cat("The probability of winning in at least 7 moves is ", sum(P1)*100, "%")
```


```{r}

library(dplyr)
library(ggplot2)

data.frame(x = 0:20, prob = dnbinom(x = 0:20, size = r, prob = p)) %>%
  mutate(Failures = ifelse(x == n, n, "other")) %>%
ggplot(aes(x = factor(x), y = prob, fill = Failures)) +
  geom_col() +
  geom_text(
    aes(label = round(prob,2), y = prob + 0.01),
    position = position_dodge(0.9),
    size = 3,
    vjust = 0
  ) +
  labs(title = "Probability of r = 12 Successes in X = 20 Trials",
       subtitle = "NB(3,.2)",
       x = "Failed Trials (X - r)",
       y = "Probability") 
```
```{r}
cum_prob <- data.frame(x = 1:20, 
           pmf = dnbinom(x = 1:20, size = r, prob = p),
           cdf = pnbinom(q = 1:20, size = r, prob = p, lower.tail = TRUE))
cum_prob
cum_prob %>%
ggplot(aes(x = factor(x), y = cdf)) +
  geom_col() +
  geom_text(
    aes(label = round(cdf,2), y = cdf + 0.01),
    position = position_dodge(0.9),
    size = 3,
    vjust = 0
  ) +
  labs(title = "Cumulative Probability of X = x failed trials to achieve 12nd success",
       subtitle = "NB(12,.6)",
       x = "Failed Trials (x)",
       y = "probability") 
```

#### More about R Functions

R Functions dnbinom, pnbinom, and rnbinom

Random varaible X is distributed X∼NB(r,p) with mean μ=rp and variance σ2=r(1−p)p2 if X is the count of independent Bernoulli trials required to achieve the rth successful trial when the probability of success is constant p. 

The probability of X=n trials is f(X=n)=(n−1r−1)pr(1−p)n−r.

  - R function dnbinom(x, size, prob) is the probability of x failures prior to the rth success (note the difference) when the probability of success is prob.
  - R function pgeom(q, prob, lower.tail) is the cumulative probability (lower.tail = TRUE for left tail, lower.tail = FALSE for right tail) of less than or equal to q failures prior to success.
  - R function rgeom(n, size, prob) returns n random numbers from the geometric distribution x~geom(prob).
  - R function qgeom(p, prob, lower.tail) is the number of failures at the qth percentile (lower.tail = TRUE).
