---
title: "STATQ8_testF"
author: "Mariana Higashi Sakamoto"
date: "16/01/2022"
output: html_document
---
## Question 8. 

Data was collected on the amount of rain per day (in millimeters), for 14 days, for two different places. The researcher noticed that place A appears to have greater variability in the rain amount, compared to place B. 
In this sense, they want to test the hypothesis that the variability in the amount of rain is significantly greater in A than in B. 

Perform the F-test to test this hypothesis.

```{r}
library()

place_A <- c(8.9,7.7,8.6,3.9,7.6,10.2,9.6	,8.9,9.6,5.5,0.5,1.5,1.5,4.00)
place_B <- c(5.6,4.9,6.6,5.9,6.5,5.9,3.6,5.6,8.8,7.8,9.9,11,8.3,5.5)

df_rain <- data.frame(place_A, place_B)
print(df_rain)

```
## Answer
We want to test the hipothesis of place A having a greater variability than B.
  $h_0$: The variancies are statistically the same
  $h_1$: The variancies are statistically different

In order to do so, we can calculate the F-statistic of this two variances:

$$F = \dfrac {S_A^2} {S_B^2}$$ 
The degrees of freedom are $n_A−1$ (for the numerator) and $n_B−1$ (for the denominator).

F-test is very sensitive to departure from the normal assumption. You need to check whether the data is normally distributed before using the F-test.

Shapiro-Wilk test can be used to test whether the normal assumption holds. It’s also possible to use Q-Q plot (quantile-quantile plot) to graphically evaluate the normality of a variable. Q-Q plot draws the correlation between a given sample and the normal distribution.

```{r}
qqnorm(df_rain$place_A, pch = 1, frame = FALSE)
qqline(df_rain$place_A, col = "steelblue", lwd = 2)

shapiro.test(df_rain$place_A) #since p-value is bigger than 5% it can be considered normal

qqnorm(df_rain$place_B, pch = 1, frame = FALSE)
qqline(df_rain$place_B, col = "steelblue", lwd = 2)

shapiro.test(df_rain$place_B)#since p-value is bigger than 5% it can be considered normal
```
 Now that normality is checked, we can procceed to the F-test 

```{r}
# Calculating each variance
var_A <- var(place_A)
var_B <- var(place_B)

F_stat <- var_A/var_B
print(F_stat)

var.test(place_A, place_B, alternative = "greater")

```
Because the p-value is less than 5% significance, the null hypothesis is rejected.

Another way to test the hypothesis is by calculatinf the critical F-value

```{r}
# Critical F-value
qf(p = 0.05, df1 = 13, df2 = 13, lower.tail=F)
```

Because the critical F-value is lower than the F-statistic, the null hypthesis is rejected

