---
title: "Question 5 - Statistics"
author: "Mariana Higashi Sakamoto"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Question 5

5. (Source: Fávero and Belfiore, 2017, Cap. 5) Suppose in a certain hospital, 3 people are operated daily with a stomach surgery, following a Poisson distribution. Calculate the probability of 28 people being operated in the next week (7 working days).


#### Review: Poisson Distribution
The Poisson distribution can be applied to systems with a large number of possible events, each of which is rare. The number of such events that occur during a fixed time interval is, under the right circumstances, a random number with a Poisson distribution.

$$  f(k,\lambda) = P(X=k)=\dfrac{\lambda^ke^{-\lambda}}{k!} $$

The equation can be adapted if, instead of the average number of events ${\displaystyle \lambda} $, we are given the average rate r at which events occur. Then ${\displaystyle \lambda =rt}$, and

$$ P(k, t)= \dfrac{ (rt)^k.e^{-rt}}{k!} $$
#### Solution
```{r}

poisson <- function(lambda,k) {
  p<-(lambda)^k*exp(-lambda)/factorial(k)*100
  return (p)
} 

poisson(lambda=3, k = 28/7)

dpois(28/7, 3)

plot(data.frame(c(0:10),dpois(c(0:10),3)), type = "b", lty = 2) + abline(v=28/7, col="red")


```

